\section*{Appendix A: Team Members and Other Information}
\addcontentsline{toc}{section}{Appendix A: Team Members and Other Information}

\baades{This section is mandatory and must include all of the following
components. If a particular subsection is not applicable, state “NONE”.}

\vspace{1ex}

\noindent
\textbf{Team Member Identification}:

\vspace{1ex}

\baades{Provide a list of all team members including the
prime, subcontractor(s), and consultant(s), as applicable. Identify specifically
whether any are a non-US organization or individual, FFRDC and/or Government
entity.}

\begin{centering}

%\small
\begin{tabular}{|p{1.8in}|p{1in}|p{1.1in}|p{0.7in}|p{0.8in}|p{0.7in}|}
\hline
 \textbf{Name} &  \textbf{Role} & \textbf{Organization} & \textbf{Non-US Org?}  & \textbf{Non-US Ind?} &  \textbf{FFRDC or Gov} \\
 \hline
Craig A. Knoblock & Prime & USC & N & N & N\\ \hline
Michael Orosz & Prime & USC & N &  N & N \\ \hline
Satish Thittamaranahalli & Prime & USC & N &  Y & N \\ \hline
Ryan Goodfellow & Prime & USC & N &  N & N \\ \hline
Anoop Kumar & Prime & USC & N & N & N \\ \hline
Satyandra Gupta & Prime & USC & N & N & N \\ \hline
Pierluigi Nuzzo & Prime & USC & N & Y & N \\ \hline
Petros Ioannou & Prime & USC & N & N & N \\ \hline
Chitta Baral & Subcontractor & ASU & N & N & N \\ \hline
Matt Barry & Subcontractor & Kestrel Technology & N & N & N \\ \hline
Douglas Smith & Subcontractor & Kestrel Technology & N & N & N \\ \hline
Henny Sipma & Subcontractor & Kestrel Technology & N & Y & N \\ \hline
\end{tabular} 
\end{centering}

\vspace{1ex}

\noindent
\textbf{Government or FFRDC Team Member Proof of Eligibility to Propose}: NONE

\baades {If
none of the team member organizations (prime or subcontractor) are a
Government entity or FFRDC, state “NONE”.}

\vspace{1ex}

\noindent
\textbf{Government or FFRDC Team Member Statement of Unique Capability}: NONE

\vspace{1ex}

\noindent
\textbf{Organizational Conflict of Interest Affirmations and Disclosure}: NONE

\vspace{1ex}

\noindent
\textbf{Intellectual Property (IP)}: 
\baades {
If no IP restrictions are intended, state “NONE”.
The Government will assume unlimited rights to all IP not explicitly identified as
having less than unlimited rights in the proposal.
For all technical data or computer software that will be furnished to the
Government with other than unlimited rights, provide (per Section VI.B.1) a list
describing all proprietary claims to results, prototypes, deliverables or systems
supporting and/or necessary for the use of the research, results, prototypes
and/or deliverables. Provide documentation proving ownership or possession of
appropriate licensing rights to all patented inventions (or inventions for which a
patent application has been filed) to be used for the proposed project.
}
\begin{centering}

%\small
\begin{tabular}{|p{2.1in}|p{1.2in}|p{1.4in}|p{2in}|}
\hline
\multicolumn{4}{|c|}{COMMERCIAL ITEMS }\\ \hline 
 \textbf{Technical Data, Computer Software To be Furnished With Restrictions} &  \textbf{Basis for Assertion} & \textbf{Asserted Rights Category} & \textbf{Name of Person Asserting Restrictions}  \\  \hline
KT Advance & Developed with mixed funding. & Restricted & David Kulich, Contracts Manager, Kestrel technology, LLC.\\ \hline
\end{tabular} 
\end{centering}

\vspace{1ex}

\noindent
\textbf{Human Subjects Research (HSR)}: NONE

\vspace{1ex}

\noindent
\textbf{Animal Use}: NONE

\vspace{1ex}

\noindent
\textbf{Representations Regarding Unpaid Delinquent Tax Liability or a Felony
Conviction under Any Federal Law}: 
%NONE

\begin{enumerate}
\item
The proposer is  not a corporation that has any unpaid Federal tax liability that has been assessed, for which all judicial and administrative remedies have been exhausted or have lapsed, and that is not being paid in a timely manner pursuant to an agreement with the authority responsible for collecting the tax liability,
\item
The proposer is not a corporation that was convicted of a felony criminal violation under a Federal law within the preceding 24 months.
\end{enumerate}

\vspace{1ex}

\noindent
\textbf{Cost Accounting Standards (CAS) Notices and Certification}:
\baades{
For any proposer who submits a proposal which, if accepted, will result in a CAS-compliant
contract, must include a Disclosure Statement as required by 48 CFR
9903.202. The disclosure forms may be found at
http://www.whitehouse.gov/omb/procurement\_casb
If this section is not applicable, state “NONE”. For further information regarding
this subject, please see www.darpa.mil/work-with-us/additional-baa.
}
NONE
